Fasano Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov in \proglang{R}

### 2020-12-19 journalMS/article.tex
updated references to 2-D KS equations

Kolmogorov and Smimov work defined the cumulative distribution for a random D-stat as:

@@

Similar to the 1-D KS test, the obvious solution to extend the theory into higher dimensional would be to define the maximal cumulative difference between the two 2-D distributions. This however, presents an issue as the commutative distribution function is not well defined in more than one dimension\citep{Peacock1983}.

>>>>

Kolmogorov and Smimov work defined the cumulative distribution for a random D-stat, which was later refined by Kendall and Stuart~\citep{Kendall1946}:

@@

Similar to the 1-D KS test, the obvious solution to extend the theory into higher dimensional would be to define the maximal cumulative difference between the two 2-D distributions. This however, presents an issue as the commutative distribution function is not well defined in more than one dimension. In N dimensional space there are $2^{N}-1$ independant ways of defining the cumlative distribution function\citep{Peacock1983}.

ADD FIGURE for showing the 4 ways (3 independent ways) of defining the cummaltive distribution in 2-D.
$P(x < X, y < Y) = 1 - P(x > X, y > Y); P(x < X, y > Y); P(x > X, y < Y)$
